Colonies - Compute Continuums across Platforms

### 2023-06-02 paper_2023/paper.tex
improved related work section

\section{Related work}
Workflow management has been extensively studied in both academic and industrial settings with numerous approaches \cite{scafe, synapse, service_wfs, schmitt2022workflow, GarciaRepresa1740746, Ouyang2010, NIKOLOV2021100440, workflow_in_bigdata} proposed to address the challenges in this field. Recently, Apache Airflow \cite{apache_airflow} has become a popular open-source workflow management system for handling data engineering pipelines. Like Colonies, Apache Airflow enables developers to create custom operators and executors that can be integrated with various systems. Additionally, Apache Airflow offers an HTTP API that makes it possible to develop Software Development Kits (SDKs) in various programming languages. However, Apache Airflow must be integrated with a message broker, such as RabbitMQ \cite{rabbitmq} or Kafka \cite{apache_kafka} to implement task queues, resulting in a more complex architecture than Colonies. Furthermore, Colonies is based on a distributed microservice architecture that makes it more suitable for DevOps software development. As Colonies is loosely coupled, executors can be implemented and dynamically deployed on the Internet without reconfiguring the workflow engine.

@@

Today, utilization of serverless computing is experiencing a significant growth \cite{cognit}, primarily due to its potential to liberate developers from the burden of managing underlying cloud infrastructures. Attempts are currently being made to implement serverless workflow management systems. For example, OpenWolf \cite{openwolf} is a serverless workflow engine designed to utilize the Function-as-a-Service (FaaS) paradigm to compose complex scientific workflows. It is based on OpenFaaS \cite{openfaas}, which allows functions to run on Kubernetes clusters.

Colonies can also be used to implement serverless workflow management systems. This will be further discussed in Section \ref{faas}. However, in contrast to previous work, Colonies is designed to be platform independent and does hence not require container orchestration platforms like Kubernetes. By using a zero-trust security protocol, functions can be securely executed by distributed executors deployed anywhere on the Internet.

Currently, microservices are primarily used to implement large-scale web applications or Internet applications requiring high-availability. It has not yet become a prevalent design principle for workload management or implementation of HPC applications. Instead, simple job scripts are commonly used. J. Represa et al. \cite{GarciaRepresa1740746, GarciaRepresa1640771} explore various challenges associated with developing microservice-based workflow management for industrial automation within the context of the Arrowhead project \cite{delsing2017iot}. The authors conclude that microservice-based workflow technologies are viable for industrial applications, particularly due to their inherent flexibility. The primary contribution of this paper is a comprehensive technical description of how to implement a distributed workflow engine based on microservice principles, extending beyond orchestrating microservices to execute automation tasks within one platform. The vision is to create a distributed architecture where microservices can reside anywhere on the Internet and still function as a cohesive unit to execute cross-platform workloads.

Grid computing \cite{grid_computing} is a distributed computing model that allows multiple computers, which may be geographically dispersed, to collaborate in addressing large-scale computational challenges. The Colonies framework is founded upon a grid computing model with the primary purpose of assigning tasks to distributed executors. To the best of the authors' knowledge, no previous work has integrated a microservice-oriented architecture with a grid computing model to serve as an integration point for coordinating artificial intelligence workloads across a diverse range of platforms. Additionally, Colonies is designed to function as a ledger, offering complete transparency and execution history, which is essential for implementing zero-trust security.

>>>>

\section{Related work}
Distributed runtimes enable execution of software applications on many interconnected computing resources. It provides mechanisms and services to distribute, manage, and coordinate the execution of tasks. Apache Spark \cite{spark} and Apache Flink \cite{flink} are well known examples of distributed runtimes.

Apache Spark is specifically designed for distributed data processing and analytics. It operates on distributed data sets, performing transformations and computations on those datasets. It offers a rich set of APIs and libraries for data processing. Apache Flink, on the other hand, is a distributed stream processing framework to process continuous streams of data in real-time. Flink is based on a dataflow programming model and is commonly used in real-time data analytics applications. In contrast, Colonies focuses primarily on workflow management. It provides a distributed runtime environment that facilitates task execution and coordination across platforms. Unlike Spark and Flink, which primarily operate on distributed data sets or data streams, Colonies emphasizes execution and coordination of computational tasks across platforms. By enabling the execution of composable functions, Colonies aims to tackle challenges related to portability, automation, scalability, and security in heterogeneous computing environments.

Workflow management has been extensively studied in both academic and industrial settings with numerous approaches \cite{scafe, synapse, service_wfs, schmitt2022workflow, GarciaRepresa1740746, Ouyang2010, NIKOLOV2021100440, workflow_in_bigdata} proposed to address the challenges in this field. Recently, Apache Airflow \cite{apache_airflow} has become a popular open-source workflow management system for handling data engineering pipelines. Similar to Colonies, Apache Airflow enables developers to create custom operators and executors that can be integrated with various systems. Additionally, Apache Airflow offers an HTTP API that makes it possible to develop Software Development Kits (SDKs) in various programming languages. However, Apache Airflow must be integrated with a message broker, such as RabbitMQ \cite{rabbitmq} or Kafka \cite{apache_kafka} to implement task queues, resulting in a more complex architecture than Colonies. Moreover, Airflow is primarily designed to be used within one single platform, e.g. a Hadoop platform.

@@

Today, utilization of serverless computing is experiencing a significant growth \cite{cognit}, primarily due to its potential to liberate developers from the burden of managing underlying cloud infrastructures. Attempts are currently being made to implement serverless workflow management systems. For example, OpenWolf \cite{openwolf} is a serverless workflow engine designed to utilize the Function-as-a-Service (FaaS) paradigm to compose complex scientific workflows. It is based on OpenFaaS \cite{openfaas}, which allows functions to run on Kubernetes clusters. Colonies can also be used to implement serverless workflow management systems. This will be further discussed in Section \ref{faas}. However, in contrast to previous work, Colonies is designed to be platform independent and does not require a container orchestration platform like Kubernetes. By using a zero-trust security protocol, functions can be securely executed by distributed executors deployed anywhere on the Internet.

Colonies is based on a distributed microservice architecture, which makes it suitable for DevOps software development. Currently, microservices are primarily used to implement large-scale and high-availability applications. It has not yet become a prevalent design principle for workload management or implementation of HPC applications. Instead, simple job scripts are commonly used. J. Represa et al. \cite{GarciaRepresa1740746, GarciaRepresa1640771} explore various challenges associated with developing microservice-based workflow management for industrial automation within the context of the Arrowhead project \cite{delsing2017iot}. The authors conclude that microservice-based workflow technologies are viable for industrial applications, particularly due to their inherent flexibility. The primary contribution of this paper is a comprehensive technical description of how to implement a distributed workflow engine based on microservice principles, extending beyond orchestrating microservices to execute automation tasks within one platform. The vision is to create a distributed architecture where microservices can reside anywhere on the Internet and still function as a cohesive unit to execute cross-platform workloads.

Grid computing \cite{grid_computing} is a distributed computing model that allows multiple computers, which may be geographically dispersed, to collaborate in addressing large-scale computational challenges. The Colonies framework is founded upon a grid computing model with the primary purpose of assigning tasks to distributed executors. To the best of the authors' knowledge, no previous work has integrated a microservice-oriented architecture with a grid computing model to serve as an integration point for coordinating workloads. Additionally, Colonies is also designed to function as a ledger, offering complete transparency and execution history, which is essential for implementing zero-trust security.
